Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-02-26 paper.tex
Updates in data preparation

% How does GOES 7 only effect result.

@@

\section{Results}
Figure \ref{AllData} shows values of solar wind averages and mass density used in this study.

Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.  A scatter plot of these two lines is shown in Figure~\ref{ccplot}.  The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50$~nT and $\rho_{eq}=40$~amu/cm$^3$}.
\label{AllData}
\end{figure}

>>>>

@@

Figure \ref{AllData} shows values of solar wind averages and mass density from GOES 6.  The corresponding 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29

Figure~\ref{ccplot} shows the long-term trends of GOES 6 based $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.  A scatter plot of these two lines is shown in Figure~\ref{ccplot}.  The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.

\section{Results}

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Reconstruction} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 40$~amu/cm$^3$}.
\label{AllData}
\end{figure}
